Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with \pkg{ACSNMineR} and \pkg{RNaviCell} Packages

### 2016-09-20 jss/Deveau.tex
Minor paper corrections
- space around "="
- Added U830 affiliation

# Create list of genes differentially expressed between ER positive and 
# ER negative samples using moderated t-test statistics 
design <- model.matrix(~factor(pdat$er == '1'))
lmFit(eset, design) -> fit
eBayes(fit) -> ebayes
toptable(ebayes, coef=2,n=25000) -> tt
which(tt$adj < 0.05) -> selection
rownames(tt[selection,]) -> probe_list
mget(probe_list, env=hgu133aSYMBOL) -> symbol_list
symbol_list <- as.character(symbol_list)

@@

\address{
  Paul Deveau\\
  Computational Systems Biology of Cancer, Institut Curie\\
  26, rue d'Ulm 75248 Paris\\
  France\\
}
\email{paul.deveau@curie.fr}

>>>>

# Create list of genes differentially expressed between ER positive and 
# ER negative samples using moderated t-test statistics 
design <- model.matrix(~factor(pdat$er == '1'))
lmFit(eset, design) -> fit
eBayes(fit) -> ebayes
toptable(ebayes, coef=2,n=25000) -> tt
which(tt$adj < 0.05) -> selection
rownames(tt[selection,]) -> probe_list
mget(probe_list, env = hgu133aSYMBOL) -> symbol_list
symbol_list <- as.character(symbol_list)

@@

\address{
  Paul Deveau\\
  Computational Systems Biology of Cancer, Institut Curie\\
  Genetics and Biology of Cancers, Institut Curie\\
  26, rue d'Ulm 75248 Paris\\
  France\\
}
\email{paul.deveau@curie.fr}
